HPC--101\\Onboarding

### 2020-09-10 OOD/sections/00_title.tex
addition of open ondemand slides

\title[HPC--101]{HPC--101\\Onboarding} % The short title appears at the bottom of every slide, the full title is only on the title page

\author{Director: Gwen Jacobs\\Sean Cleveland, Adriana Comerford,\\Ron Merrill, David Schanzenbach}
%\author{Director: Gwen Jacobs\\Sean Cleveland, Adriana Comerford, Jennifer Geis,\\Ron Merrill, David Schanzenbach}
\institute[University of {\hawaii} -- ITS--CI] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
Information Technology Services \\
{\ci} \\
University of {\hawaii} \\ % Your institution for the title page
\medskip
\textbf{\url{https://www.hawaii.edu/its/ci/}}\\
\textbf{\textit{uh-hpc-help@lists.hawaii.edu}} % Your email address
}
\date{\today} % Date, can be changed to a custom date

>>>>

\title[Open OnDemand]{Open OnDemand} % The short title appears at the bottom of every slide, the full title is only on the title page

\author{}
%\author{Director: Gwen Jacobs\\Sean Cleveland, Adriana Comerford, Jennifer Geis,\\Ron Merrill, David Schanzenbach}
\institute[University of {\hawaii} -- ITS--CI] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
Information Technology Services \\
{\ci} \\
University of {\hawaii} \\ % Your institution for the title page
\medskip
\textbf{\url{https://www.hawaii.edu/its/ci/}}\\
\textbf{\url{http://datascience.hawaii.edu/}}\\
\textbf{\textit{uh-hpc-help@lists.hawaii.edu}} % Your email address
}
\date{\today} % Date, can be changed to a custom date

### 2020-09-10 hpc_101/sections/01_intro.tex
addition of open ondemand slides

\section[University of Hawai'i High Performance Compute Cluster]{University of Hawai'i High Performance Compute Cluster}
\begin{frame}
    \frametitle{University of {\hawaii} High Performance Compute Cluster}
    \begin{itemize}
    \item The University~of~{\hawaii} High Performance Compute Cluster~({\uhhpc}) is \textbf{free} to use for all active faculty, staff, and students affiliated with the University of {\hawaii}
    \item Community acquired nodes are equally accessible to all users
    \item Nodes purchased through the {\textbf{condo program}} are shared with the community, but priority is given to the node owner and their agents
		\item Nodes may be {\textbf{leased}} from the community pool
		\item Additional permanent storage can be leased with up to a five year contract by faculty \& staff
    \end{itemize}
		\begin{block}{UH-HPC Resource Summary}
  \begin{table}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tabular}{l||l||l||l||l||l||l||l}
      %  \multicolumn{8}{c}{ {\large {\textbf{UH-HPC Resource Summary} } } } \\ 
			\toprule

              {}               & \thead{\textbf{Nodes}} & \thead{\textbf{CPU Cores}} & \thead{\textbf{Memory}} & \thead{\textbf{GPUs}} & \thead{\textbf{Home/Group Space}} & \thead{\textbf{Scratch Space}} & Storage for lease \\ 
							\midrule  \midrule %\hline
        \thead{\textbf{Total}} & 297                    & 6,308                      & 50 TB                   &  56                   & 80 TB                             &  150 TB                        & 1 PB              \\ %\hline
				\bottomrule
      \end{tabular}%
    }
  \end{table}
	\end{block}
\end{frame}

@@

  \begin{block}{Online documents \& FAQ}
    Users are encouraged to look through the online documentation \& FAQ prior to contacting ITS-CI directly.  Many questions we receive are repeat questions and we try to capture them in our FAQ~\\
    \href{https://www.hawaii.edu/its/ci/xcat/}{xCAT cluster information, policies \& FAQ}
  \end{block}
  \begin{block}{Contact Information}
    If your question is not answered in our online documentation, please contact us at: UH-HPC-Help@lists.hawaii.edu

>>>>

\section[University of Hawai'i High Performance Compute Cluster]{University of Hawai'i High Performance Compute Cluster}
\begin{frame}
    \frametitle{University of {\hawaii} High Performance Compute Cluster}
    \begin{itemize}
    \item The University~of~{\hawaii} High Performance Compute Cluster~({\uhhpc}) is \textbf{free} to use for all active faculty, staff, and students affiliated with the University of {\hawaii}
    \item Community acquired nodes are equally accessible to all users
    \item Nodes purchased through the {\textbf{condo program}} are shared with the community, but priority is given to the node owner and their agents
		\item Nodes may be {\textbf{leased}} from the community pool
		\item Additional permanent storage can be leased by faculty \& staff
    \end{itemize}
		\begin{block}{UH-HPC Resource Summary}
  \begin{table}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tabular}{l||l||l||l||l||l||l||l}
      %  \multicolumn{8}{c}{ {\large {\textbf{UH-HPC Resource Summary} } } } \\ 
			\toprule

              {}               & \thead{\textbf{Nodes}} & \thead{\textbf{CPU Cores}} & \thead{\textbf{Memory}} & \thead{\textbf{GPUs}} & \thead{\textbf{Home/Group Space}} & \thead{\textbf{Scratch Space}} & Storage for lease \\ 
							\midrule  \midrule %\hline
        \thead{\textbf{Total}} & 298                    & 6,308                      & 50 TB                   &  64                   & 80 TB                             &  150 TB                        & 1 PB              \\ %\hline
				\bottomrule
      \end{tabular}%
    }
  \end{table}
	\end{block}
\end{frame}

@@

  \begin{block}{Online documents \& FAQ}
    Users are encouraged to look through the online documentation \& FAQ prior to contacting ITS-CI directly.  Many questions we receive are repeat questions and we try to capture them in our FAQ.~\\
		\begin{itemize}
		\item \href{http://datascience.hawaii.edu/hpc/}{Information \& policies}
		\item \href{http://go.hawaii.edu/jdG}{FAQ}
		\item \href{http://go.hawaii.edu/3A8}{Video Tutorials}
		\end{itemize}
  \end{block}
  \begin{block}{Contact Information}
    If your question is not answered in our online documentation, please contact us at: UH-HPC-Help@lists.hawaii.edu
